---
#
# Required Information --------------------------------------------------------
# change lines 5 - 15
title: "Phosphate dynamics in iron treated peat ditches"
type: "Master's Thesis"
author: "Harm van Kuppevelt"
matriculation_number: "4061985"
date: "June, 2021"
university: "Utrecht University"
institute: "Faculty of Geosciences" 
chair: "Department of Earth sciences"
advisor1: "Dr. Thilo Behrends"
advisor2: "Melanie Münch Msc."            
program: "Master of Earth Science"
#
# Optional Information --------------------------------------------------------
# comment out if unnecessary
chair2: "Geochemistry"
abstract: |  
  `r if(knitr:::is_latex_output()) paste(readLines("prelim/00-abstract.Rmd"), collapse = '\n  ')`
acknowledge: |  
  `r if(knitr:::is_latex_output()) paste(readLines("prelim/00-acknowledge.Rmd"), collapse = '\n  ')`
lot: true                              # list of tables
lof: true                              # list of figures
link-citations: true
bibliography: bib/references.bib       # bibliography file
#
# Rendering Options -----------------------------------------------------------
#
knit: "bookdown::render_book"
output: 
  huwiwidown::thesis_pdf  
space_between_paragraphs: true       # if you want spaces bt paragraph
# header-includes:     # if including additional latex packages or commands
  # - \setlength{\parindent}{17pt}
---

<!--
Above is the YAML (YAML Ain't Markup Language) header that includes a lot of
metadata used to produce the document.  Be careful with spacing in this header!
If you'd like to include a comment that won't be produced in your resulting file
enclose it in a block like this.
-->

<!--
If you receive a duplicate label error after knitting, make sure to delete the
index.Rmd file and then knit again.
-->

```{r include_packages, include = FALSE}
# This chunk ensures that the `huwiwidown` package is installed and loaded. This
# package includes the template files for the thesis.
if (!require(devtools)) {
  install.packages("devtools", repos = "http://cran.rstudio.com")
}
if (!require(huwiwidown)) {
  devtools::install_github("phister/huwiwidown")
  library(huwiwidown)
  

}
library(readxl)
library(here)
library(tidyverse)
library(ggplot2)
library(reshape2)
```

<!-- 
The {.unnumbered} option here means that the introduction will be "Section  0."
You can also use {-} for no numbers on section. 
-->

<!--
The body of the thesis starts underneath the text below. Feel free to delete
everything below this.
-->

# Preface {-}

Welcome to the thesis template. This template is based on (and in many places 
copied directly from) the HU Berlin School of Business and Economics LaTeX 
template, but hopefully it will provide a nicer interface for those that have
never used LaTeX before. 


<!--chapter:end:index.Rmd-->

# Introduction

* What is the subject of the study? Describe the  problem.

* What is the purpose of the study (working hypothesis)?

* What do we already know about the subject (literature review)? Use citations:
  @lingenfelser2011systematic shows that... Alternative Forms of the Wald test are
  considered [@kuncheva2004combining].
  
* What is the innovation of the study?

* Provide an overview of your results.

* Outline of the paper:\
  _The paper is organized as follows. The next section describes the model
  under investigation. Section "[Data]" describes the data set
  and Section "[Results]" presents the results. Finally, Section
  "[Conclusion]" concludes._
* The introduction should not be longer than 4 pages.

<!--chapter:end:sections/01-intro.Rmd-->

# Methodology



[^1]: Here is an example of a footnote.

<!--chapter:end:sections/02-method.Rmd-->

# Results

```{r pwgraphs, include = FALSE, echo=FALSE}


# import raw data


IC_raw_data <- read_excel(path.expand(here("index","data", "IC_raw_data.xlsx")))
pw_photometric <-  read_excel(path.expand(here("index","data", "pw_P_photometric.xlsx")))

# Transform the raw data to middle duplicates.
ICplotdata  <- IC_raw_data %>% 
  filter(str_detect(sample,"pw|sw")) %>% 
  group_by(sample) %>% 
  mutate(P = (mean(Phosphate)*1000)/94.9714, "SO" = mean(Sulphate)*1000/96.06, NO = mean(Nitrate)*1000/62.004, "Br" = mean(Bromide)*1000/79.9, "Fl" = mean(Fluoride)*1000/19, "Cl" = mean(Chloride)*1000/35.45 ) %>%
  distinct(sample, .keep_all = TRUE) %>% 
  mutate(treated =
      case_when(
        str_detect(sample,"A|C")  ~ "treated",
        str_detect(sample,"B|D")  ~ "nontreated")) %>% left_join(
  pw_photometric,
  by = c("sample" = "Sample"),
  copy = FALSE,
  suffix = c(".IC", ".photometric"),
  keep = FALSE
) %>%  group_by(location) %>% arrange(cm_below_swi) 

# reshape data.
molten_IC_core_data <- ICplotdata %>% select("location", "sample", "cm_below_swi", "SO" : "treated") %>% 
melt(id.vars = c("location", "sample", "cm_below_swi", "treated"), 
     measured_.vars = c(  
                         "SO", 
                         "NO",
                         "Br",
                         "Fl", 
                         "Cl"), na.rm = TRUE)

nest_IC_pw_depth <- molten_IC_core_data %>% group_by(variable) %>% nest()

# plot profiles by parameter

Lables = as_labeller( c( "P"  = "PO[4]^'3-'",                      
   "SO" = "SO[4]^'2-'", 
   "NO" = "NO[3]^'-'",
   "Br" = "Br^'-'",
   "Fl" = "F^'-'", 
   "Cl" = "Cl^'-'"), default =  label_parsed )

IC_profile_plots <- ggplot(molten_IC_core_data, mapping = aes(
                        x = value,
                        y = cm_below_swi ,
                        color = location,
                        shape = location)
         ) +
       
       scale_color_manual( values=c("A" = "red", "B" = "blue", "C" = "red", "D" = "blue")) +
       scale_shape_manual( values=c("A" = 16, "B" = 1, "C" = 17,  "D" = 2)) +
      scale_y_reverse() +
       geom_point() + 
       geom_path() +
       facet_grid(cols = vars(variable), scales = "free_x", labeller = Lables) +
       labs(  x = expression(paste("concentration in ",mu,"mol/L")), 
              y = "Depth in cm",
              title = "pw profiles measured with IC") +
      theme_classic() +
      theme(aspect.ratio = 2. ,
            axis.text.y   = element_text(size=14),
            axis.text.x   = element_text(size=14),
            axis.title.y  = element_text(size=14),
            axis.title.x  = element_text(size=14),
            strip.text.y   = element_text(size=14),
            strip.text.x   = element_text(size=14),
            panel.background = element_blank(),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.border = element_rect(colour = "black", fill=NA, size=1)
            )

ggsave(paste("IC_profiles.png",sep=""), plot =IC_profile_plots, path = path.expand(here("index","figures")),

       width =30, height = 18,units = "cm",dpi = 600)

```



``` {r ICinc, include = FALSE, echo = FALSE}

incubationgraph <- read_excel(here("index","data","incubationgraph.xlsx"))

# middle duplicates for IC data
IC_inc_data <- 
  IC_raw_data %>% 
  filter(str_detect(sample,'inc')) %>% 
  group_by(sample) %>% 
  mutate(P = (mean(Phosphate)*1000)/94.9714, 
         "SO" = mean(Sulphate)*1000/96.06, 
         NO = mean(Nitrate)*1000/62.004, 
         "Br" = mean(Bromide)*1000/79.9, 
         "Fl" = mean(Fluoride)*1000/19,
         "Cl" = mean(Chloride)*1000/35.45) %>% 
  distinct(sample, .keep_all = TRUE) 


# Join IC and photometric data, and add treated and oxic status foor all cores.
inc_data <- 
full_join(
  incubationgraph,
  IC_inc_data,
  by = c("samplenr" = "sample"),
  copy = FALSE,
  suffix = c(".photometric", ".IC"),
  keep = FALSE
) %>% 
  mutate(HS = 1.1*(((H2SuM*1.13759603802245)/0.026915542)/1000)
) %>% 
  mutate(oxic_state =
      case_when(
        str_detect(samplenr,"2\\.")  ~ "oxic",
        str_detect(samplenr,"3\\.")  ~ "anoxic")) %>% 
  mutate(treated =
      case_when(
        str_detect(samplenr,"A|C")  ~ "treated",
        str_detect(samplenr,"B|D")  ~ "nontreated"))  %>% 
  mutate(Location =
      case_when(
        str_detect(samplenr,"A")  ~ "A",
        str_detect(samplenr,"-B")  ~ "B",
        str_detect(samplenr,"-\\C")  ~ "C",
        str_detect(samplenr,"-\\D")  ~ "D")) 

# slope of NH4 line

initinc <- inc_data %>% filter(time < 10 ) %>% mutate(NH4mol = 0.001*NH4*`volume_(ml)` ) %>% view
initplot <- ggplot( initinc,
       mapping = aes(x = time , 
                     y = NH4mol, 
                     color = treated, 
                     shape = Location, 
                     by = Core.photometric)
       ) + 
  scale_color_manual( values=c("treated" = "red", "nontreated" = "blue")) +
  scale_shape_manual( values=c("A" = 16, "B" = 1, "C" = 17,  "D" = 2)) +
  geom_point() + 
  geom_line() + 
  stat_smooth(method = "lm") +
  facet_grid(~ oxic_state)
  

show(initplot)

initslopes <- initinc %>%  group_by(Core.photometric) %>% 
  summarize(NH4slope = coef(lm(NH4mol ~ time))[2]
            ) %>% filter(str_detect(Core.photometric,"3\\.")) %>%  add_column(
O2slope = c(-0.172133,
-0.404987,
-0.360635,
-0.0793467,
-0.370374,
-0.174982,
-0.227892,
-0.167105
)) %>% mutate(O2_umol_day = -1000*(O2slope*24)/31.9988) 

initreg <- ggplot(initslopes, 
      mapping = aes( 
           y=NH4slope, 
           x=O2_umol_day),
       scale_x_discrete(position = 'top')) +
    geom_point(
      stat = "identity", position = position_stack(reverse=TRUE),color="black") 
    
show(initreg)

# reshape the data by melting all variables, and grouping them by parameter.

molten_inc <- inc_data %>% select("Core.photometric", 
                                  "samplenr",
                                  "time", 
                                  "HS", 
                                  "FeTot(uM)", 
                                  "Preal(uM)", 
                                   "NH4", 
                                   "SO",
                                   "NO",
                                  "oxic_state", 
                                  "treated", 
                                  "Location") %>% 
melt(id.vars = c("Core.photometric","samplenr","time", "oxic_state", "treated","Location"), 
     measured_.vars = c( "HS", 
                         "FeTot(uM)", 
                         "Preal(uM)", 
                         "NH4", 
                         "SO",
                         "NO"), na.rm = TRUE)

nest_inc <- molten_inc %>% group_by(variable) %>% nest()

# create plots for all parameters
Lables = as_labeller( c(  "HS" = "HS^'-'", 
                          "FeII(uM)" = "Fe^'2+'",
                          "FeTot(uM)" = "Fe[tot]", 
                          "FeIII(uM)" = "Fe^'3+'",  
                          "Preal(uM)" = "PO[4]^'3-'",
                          "NH4" = "NH[4]^'+'",
                          "P"  = "PO[4]^'3-'",                      
                          "SO" = "SO[4]^'2-'", 
                          "NO" = "NO[3]^'-'",
                          "Br" = "Br^'-'",
                          "Fl" = "F^'-'", 
                          "Cl" = "Cl^'-'"), default =  label_parsed )

IC_incubation_graph <- 
  ggplot(molten_inc, 
       mapping = aes(x = time , 
                     y = value, 
                     color = treated, 
                     shape = Location, 
                     by = Core.photometric)
       ) + 
  scale_color_manual( values=c("treated" = "red", "nontreated" = "blue")) +
  scale_shape_manual( values=c("A" = 16, "B" = 1, "C" = 17,  "D" = 2)) +
  geom_point() + 
  geom_line() + 
  theme(aspect.ratio = 0.5,
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        strip.text.y   = element_text(size=14),
        strip.text.x   = element_text(size=14),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1)
        ) + 
  facet_grid(variable ~ oxic_state, scales = "free_y",switch = "y", labeller = Lables) + labs(title = "Incubations", x= "time (days)", y = expression(paste("concentration in ",mu,"mol/L")))

ggsave(paste("IC_incubations.png",sep=""), plot =IC_incubation_graph, path = path.expand(here("index","figures")),

       width =20, height = 20,units = "cm",dpi = 600)

```



```{r Feseq, include = FALSE, echo=FALSE}
#import sequential extraction data.
Seq_extr_data <- read_excel(here("index","data","Seq_extr_data.xlsx"))


# define detection limits as given by ICP report
Detlim_Fe_MgCl <- 0.068
Detlim_Fe_HCl <- 0.021
Detlim_Fe_CDB <- 0.1071
Detlim_Fe_HNO <- 0.035
Detlim_P_MgCl <- 0.097
Detlim_P_HCl <- 0.043
Detlim_P_CDB <- 0.0976
Detlim_P_HNO <- 0.057

# density of extractants and molar weight of Fe and P
d_MgCl <- 1.0467
d_pyroP <- 1.0402
d_HCl <- 1.0152
d_CDB <- 1.0887
d_HNO <- 1.414
mw_Fe <- 55.845
mw_P <- 30.973762


# define functions to calculate umol/g sediment from raw ICP and colourimetric data.
ppm_to_umol_p_g <- function(mol_weight, 
                            Dens, 
                            total_weight, 
                            sample_weight, 
                            Dil = 10, 
                            detlim, 
                            ppm){
  
 conc <- case_when(ppm/Dil < detlim ~ 0, 
                   T ~ ((total_weight/Dens)*ppm)/(sample_weight*mol_weight) 
                    )
 return(conc)
}

mM_to_umol_p_g<- function(  Dens, 
                            total_weight, 
                            sample_weight,
                            mM){
  
 conc <- case_when(mM < 0 ~ 0,
                   T ~ ((total_weight/Dens)*mM)/(sample_weight) )
                    
 return(conc)
}

# Transform raw data.
Seq_extr_trans <-  Seq_extr_data %>% 
  mutate(
    Location = case_when(
        str_detect(Station,"A")  ~ "A",
        str_detect(Station,"-B")  ~ "B",
        str_detect(Station,"-C")  ~ "C",
        str_detect(Station,"-D")  ~ "D",
        T ~ "blank"),
    Incubation = case_when(
        str_detect(Station, "1\\.") ~ "before",
        str_detect(Station, "3\\.")  ~ "after",
        T ~ "blank" ),
    Fe_MgCl_A_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_MgCl, 
                                  total_weight = weight_MgCl_A, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_MgCl,
                                  ppm = ICP_MgCl_A_Fe),
    Fe_MgCl_B_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_MgCl, 
                                  total_weight = weight_MgCl_B, 
                                  sample_weight = sample_weight_B, 
                                  detlim = Detlim_Fe_MgCl,
                                  ppm = ICP_MgCl_B_Fe),
    Fe_pyroP_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_pyroP,
                                  Dil = 20,
                                  total_weight = weight_pyroP, 
                                  sample_weight = sample_weight_B, 
                                  detlim = Detlim_Fe_HNO,
                                  ppm = ICP_pyroP_Fe),
    Fe_HCl_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_HCl, 
                                  total_weight = weight_HCl, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_HCl,
                                  ppm = ICP_HCl_Fe),
    Fetot_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_Fetot),
    FeII_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_FeII),
    FeIII_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_FeIII),
    Fe_CDB_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_CDB, 
                                  total_weight = weight_CDB, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_CDB,
                                  ppm = ICP_CDB_Fe),
    Fe_HNO_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_HNO, 
                                  total_weight = weight_HNO, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_HNO,
                                  ppm = ICP_HNO_Fe*10),
    P_MgCl_A_calc = ppm_to_umol_p_g(mol_weight = mw_P, 
                                  Dens = d_MgCl, 
                                  total_weight = weight_MgCl_A, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_P_MgCl,
                                  ppm = ICP_MgCl_A_P),
    P_HCl_calc = ppm_to_umol_p_g(mol_weight = mw_P, 
                                  Dens = d_HCl, 
                                  total_weight = weight_HCl, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_P_HCl,
                                  ppm = ICP_HCl_P),
    P_CDB_calc = ppm_to_umol_p_g(mol_weight = mw_P, 
                                  Dens = d_CDB, 
                                  total_weight = weight_CDB, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_P_CDB,
                                  ppm = ICP_CDB_P),
    P_HNO_calc = ppm_to_umol_p_g(mol_weight = mw_P, 
                                  Dens = d_HNO, 
                                  total_weight = weight_HNO, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_P_HNO,
                                  ppm = ICP_HNO_P*10)
    ) 

# Middle all duplicates
Seq_extr_dr <-Seq_extr_trans %>% 
                  filter(Incubation != "blank") %>% 
                  group_by(Station) %>% 
                  mutate(Fe_MgCl_A = mean(Fe_MgCl_A_calc),
                         Fe_MgCl_B = mean(Fe_MgCl_B_calc),
                         Fe_HCl_FeII = mean(FeII_HCl_calc),
                         Fe_HCl_FeIII = mean(FeIII_HCl_calc),
                         Fe_CDB = mean(Fe_CDB_calc),
                         Fe_HNO = mean(Fe_HNO_calc),
                         PyroP = mean(Fe_pyroP_calc),
                         Fe_HCl_ICP = mean(Fe_HCl_calc),
                         Fe_HCl_col = mean(Fetot_HCl_calc),
                         Fe_HClminPP = mean(Fetot_HCl_calc)-mean(Fe_pyroP_calc),
                         P_MgCl_A = mean(P_MgCl_A_calc),
                         P_HCl = mean(P_HCl_calc),
                         P_CDB = mean(P_CDB_calc),
                         P_HNO = mean(P_HNO_calc)) %>% 
                  distinct(Station, .keep_all = TRUE) %>% 
                  ungroup 


# create figures 
seq_extr_A_Fe_molten <- Seq_extr_dr %>% 
                  select("depth","Location","Incubation", Fe_MgCl_A, Fe_HCl_FeII, Fe_HCl_FeIII, Fe_CDB, Fe_HNO) %>% 
                  melt(id.vars = c("depth","Location","Incubation"), variable.name = "Fraction" , na.rm = TRUE) 
                  
seq_extr_B_Fe_molten <- Seq_extr_dr %>% 
                  select("depth","Location","Incubation", Fe_MgCl_B, PyroP, Fe_HClminPP, Fe_CDB, Fe_HNO) %>% 
                  melt(id.vars = c("depth","Location","Incubation"), variable.name = "Fraction" , na.rm = TRUE) 
                  
seq_extr_A_P_molten <- Seq_extr_dr %>% 
                  select("depth","Location","Incubation", P_MgCl_A, P_HCl, P_CDB, P_HNO) %>% 
                  melt(id.vars = c("depth","Location","Incubation"), variable.name = "Fraction" , na.rm = TRUE) 

list_sq_extr_plots <-  list(seq_extr_A_Fe_molten, seq_extr_B_Fe_molten, seq_extr_A_P_molten)


for (i in 1:length(list_sq_extr_plots)) {
  
  j <- ggplot(list_sq_extr_plots[[i]], 
       aes(fill=Fraction, 
           y=value, 
           x=depth),
       scale_x_discrete(position = 'top'))+
    geom_area(
      aes(color = Fraction),
      stat = "identity", position = position_stack(reverse=TRUE))+
    geom_point(
      aes(color = Fraction),
      stat = "identity", position = position_stack(reverse=TRUE),color="black")+
    geom_line(
      aes(color = Fraction),
      stat = "identity", position = position_stack(reverse=TRUE),color="black")+
    coord_flip()+
    scale_x_reverse()+ 
    xlab("Depth (mm)")+ 
    scale_y_continuous(breaks=NULL,labels=NULL,name=NULL,sec.axis = sec_axis(~ . *1,name=expression(paste("Extracted Fe (",mu,"mol'*g DW"^-1,")"))))+
    ylab(expression(paste("Extracted Fe (",mu,"mol gDW"^-1,")")))+
    theme_classic()+
    scale_color_grey()+ 
    scale_fill_brewer(palette = "Reds",direction = -1)+
    theme(axis.title=element_text(size=28),plot.title = element_text(hjust = 0.5),
          axis.text=element_text(size=24,angle = 0, hjust = 0.5),
          panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank(),
          legend.title = element_text( size = 20),
          legend.text = element_text(size = 20)) +
    facet_grid(Location ~ Incubation)

ggsave(paste("seq_extr_Fe_",i,".png",sep=""), plot =j, path = path.expand(here("index","figures")),

       width =30, height = 50,units = "cm",dpi = 600)
  
}

eq <- function(x,y) {
  m <- lm(y ~ x)
  as.character(
    as.expression(
      substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,
                list(a = format(coef(m)[1], digits = 4),
                b = format(coef(m)[2], digits = 4),
                r2 = format(summary(m)$r.squared, digits = 3)))
    )
  )
}

seq_extr_Fe <- ggplot(Seq_extr_dr, 
      mapping = aes( 
           y=Fe_HCl_ICP, 
           x=Fe_HCl_col),
       scale_x_discrete(position = 'top')) +
    geom_point(
      stat = "identity", position = position_stack(reverse=TRUE),color="black") +
    stat_smooth(method = "lm")+
    geom_text(x = 25, y = 300, label = eq(Seq_extr_dr$Fe_HCl_col, Seq_extr_dr$Fe_HCl_ICP), parse = TRUE)
show(seq_extr_Fe)
 

```

```{r swcalc, include = FALSE, echo=FALSE}

EC_A <- c(434,	449,	433)
EC_B <- c(446,	456,	451)
EC_C <- c(379,	408,	400)
EC_D <- c(392,	397,	402)
EC <- list(EC_A, EC_B, EC_C, EC_D)

for (i in 1:4) {
 m = mean(EC[[i]])
 s = sd(EC[[i]])
 print(m)
 print(s)
  
}

t.test(EC_A, EC_B)
t.test(EC_C, EC_D)
t.test(c(EC_A, EC_B),c(EC_C, EC_D))
```

* The surface water at the treated and non treated locations was similar in composition and oxic conditions at time of sampling.
* locations A and B had a significantly higher electric conductivity (438 \muS and 451), than locations C and D (395 and 397)

* Use tables, figures (but prefer visual presentation):

  + Tables and figures should supplement (and not duplicate) the text.

  + Tables and figures should be provided with legends.

  + _Figure \@ref(fig:graph) shows how to include and reference graphics.
    The graphic must be labelled before. Files must be in __.eps__ format. You
    can do this really easily in R Markdown with `knitr::include_graphics()`_!

  + Figures can be referenced with `\@ref(fig:<name>)`, where `<name>` is the
    name of the code chunk.

```{r graph, echo=FALSE, fig.cap="Estimated residuals from model XXX. ...", out.width = "50%"}
knitr::include_graphics(here("index","figures","graph.eps"))
```
  + Tables and graphics may appear in the text or in the appendix, especially if
  there are many simulation results tabulated, but is also depends on the study
  and number of tables resp. figures. The key graphs and tables must appear in
  the text!

```{r table, echo=FALSE}
library(tidyverse)
col_names <- c(
  "3m", "6m", "1yr", "2yr", "3yr", "5yr", "7yr", "10yr", "12yr", "15yr"
)
means     <- c(
  3.138, 3.191, 3.307, 3.544, 3.756, 4.093, 4.354, 4.621, 4.741, 4.878
)
stddev    <- c(
  0.915, 0.919, 0.935, 0.910, 0.876, 0.825, 0.803, 0.776, 0.768, 0.762
)
row_names <- c("Mean", "StD")

df <- matrix(data = c(means, stddev), nrow = 2, byrow = T)
rownames(df) <- row_names
colnames(df) <- col_names
df <- data.frame(df)
knitr::kable(
  df,
  booktabs = TRUE,
  caption = "Detailed descriptive statistics of location and dispersion for 2100 observed swap rates for the period from February 15, 1999 to March 2, 2007. Swap rates measured as 3.12 (instead of 0.0312).",
  col.names = col_names, 
  escape = FALSE
) %>%
kable_styling(latex_options = c("HOLD_position")) %>%
row_spec(2, hline_after = T)
```

* Allows the reader to judge whether the sample is biased or to evaluate 
  possible impacts of outliers, for example.

* Here tables can be easily integrated using the `kable()` function in the
  `knitr` package (with perhaps some additional help from the `kableExtra`
  package). `kable()` will automatically generate a label for the table
  environment. That way you don't have to manually enter in the table in LaTex,
  you can embed tables from R code. 

* Tables can be referenced using `\@ref(label)`, where `label` is `tab:<name>`,
  where `<name>` is the code chunk label.

* The appearance may look different to tables directly typed with LaTex, due to
  limitations in `kable()`. To compare:
    \begin{table}[ht]

    \begin{center}
        {\footnotesize
        \begin{tabular}{l|cccccccccc}
            \hline \hline
                      & 3m    & 6m    & 1yr   & 2yr   & 3yr   & 5yr   & 7yr   & 10yr  & 12yr  & 15yr   \\
            \hline
                Mean   & 3.138 & 3.191 & 3.307 & 3.544 & 3.756 & 4.093 & 4.354 & 4.621 & 4.741 & 4.878  \\
                StD    & 0.915 & 0.919 & 0.935 & 0.910 & 0.876 & 0.825 & 0.803 & 0.776 & 0.768 & 0.762  \\
            \hline \hline
        \end{tabular}}
    \end{center}
    \caption{This table was handwritten with LaTeX.}
    \label{tab:table2}
    \end{table}

* R Markdown can also supports math equations just like _LaTeX_!

  + _Equation \@ref(eq:SpecDens) represents the ACs of a stationary
    stochastic process:_
    \begin{equation}
            f_y(\lambda) = (2\pi)^{-1} \sum_{j=-\infty}^{\infty}
                           \gamma_j e^{-i\lambda j}
                         =(2\pi)^{-1}\left(\gamma_0 + 2 \sum_{j=1}^{\infty}
        \gamma_j \cos(\lambda j)\right)
                                       (\#eq:SpecDens)
    \end{equation}
    _where $i=\sqrt{-1}$ is the imaginary unit, $\lambda \in [-\pi, \pi]$ is the
    frequency and the $\gamma_j$ are the autocovariances of $y_t$._

  + Equations can be referenced with `\@ref(eq:<name>)`, where name is defined
    by adding `(\#eq:<name>)` in the line immediately before `\end{equation}`.

## Review of Results

*  Do the results support or do they contradict theory ?

*  What does the reader learn from the results?

*  Try to give an intuition for your results.

*  Provide robustness checks.

*  Compare to previous research.

<!--chapter:end:sections/03-results.Rmd-->

# Discussion



<!--chapter:end:sections/04-discussion.Rmd-->

# Conclusion

* Give a short summary of what has been done and what has been found.

* Expose results concisely.

* Draw conclusions about the problem studied. What are the implications of your
  findings?

* Point out some limitations of study (assist reader in judging validity of
  findings).

* Suggest issues for future research.


<!--chapter:end:sections/05-conclusion.Rmd-->

\newpage

# References {-}

<!--
To remove the indentation of the first entry.
-->
\noindent

<!--
To create a hanging indent and spacing between entries.  These three lines may need to be removed for styles that don't require the hanging indent.
-->

\setlength{\parindent}{-0.5cm}
\setlength{\leftskip}{0.5cm}
\setlength{\parskip}{8pt}

<div id="refs"></div>

<!--
Restore to defaults
-->

\indent
\setlength{\parindent}{17pt}
\setlength{\leftskip}{0pt}
\setlength{\parskip}{0pt}

\newpage

<!--chapter:end:sections/98-references.Rmd-->

\appendix
# Appendix

Here goes the appendix!

## Figures

```{r graph2, echo=FALSE, out.extra = "", fig.cap="Estimated residuals (2) from model XXX. ...", out.width = "50%"}
knitr::include_graphics("figures/graph.eps")
```

## Tables

\begin{table}[ht]
    \begin{center}
        {\footnotesize
        \begin{tabular}{l|cccccccccc}
        \hline \hline
                        & 3m    & 6m    & 1yr   & 2yr   & 3yr   & 5yr   & 7yr   & 10yr  & 12yr  & 15yr   \\
            \hline
                Mean   & 3.138 & 3.191 & 3.307 & 3.544 & 3.756 & 4.093 & 4.354 & 4.621 & 4.741 & 4.878  \\
                Median & 3.013 & 3.109 & 3.228 & 3.490 & 3.680 & 3.906 & 4.117 & 4.420 & 4.575 & 4.759  \\
                Min    & 1.984 & 1.950 & 1.956 & 2.010 & 2.240 & 2.615 & 2.850 & 3.120 & 3.250 & 3.395  \\
                Max    & 5.211 & 5.274 & 5.415 & 5.583 & 5.698 & 5.805 & 5.900 & 6.031 & 6.150 & 6.295  \\
                StD    & 0.915 & 0.919 & 0.935 & 0.910 & 0.876 & 0.825 & 0.803 & 0.776 & 0.768 & 0.762  \\
            \hline \hline
        \end{tabular}}
    \end{center}
    \caption{Detailed descriptive statistics of location and dispersion for
    2100 observed swap rates for the period from
    February 15, 1999 to March 2, 2007. Swap rates measured as 3.12 (instead of 0.0312).}
    \label{tab:apptable}
\end{table}

\newpage

<!--chapter:end:sections/99-appendix.Rmd-->

