# Results


```{r swcalc, include = FALSE, echo=FALSE}

EC_A <- c(434,	449,	433)
EC_B <- c(446,	456,	451)
EC_C <- c(379,	408,	400)
EC_D <- c(392,	397,	402)
EC <- list(EC_A, EC_B, EC_C, EC_D)

for (i in 1:4) {
 m = mean(EC[[i]])
 s = sd(EC[[i]])
 print(m)
 print(s)
  
}

t.test(EC_A, EC_B)
t.test(EC_C, EC_D)
t.test(c(EC_A, EC_B),c(EC_C, EC_D))
```

The \textit{in situ} surface water measurements showed that both at the treated and non treated locations oxic conditions of 9.5-10.5 mg/L dissolved oxygen, and pH levels around 8. While no significant difference between treated and non-treated locations, water conditions did vary between the locations closer (C and D) and further away (A and B) from the water inlet. This variation was seen in a  significantly higher electric conductivity at locations A and B (438 $\mu$S and 451$\mu$S), than measured at locations C and D (395$\mu$S and 397$\mu$S), which correlated with sulfate concentrations. In addition, the decrease in sulfate concentration with depth in the porewater was steeper in locations C and D compared to A and B.( \@ref(fig:pwprofiles))

Differences in iron content are immediately clear when comparing the sequential extraction data, which shows that iron is much more abundant in the treated cores than in the non-treated.( \@ref(fig:seq)) The largest pool extracted in the treated sediment is the HCl extractable pool, while the orginal sediment contains predominantly iron extracted HNO$_3$. The small amount of other Fe extracted in the non-treated cores is restricted to the top few centimeter. Interestingly, the HNO$_3$ extracted Fe after treatment is lower than in the original sediment.

Phosphate abundancy in the extracted pools correlates well with total iron. While HCl extracted Fe is only a small fraction in the non-treated cores, the extracted P is largest in this pool. The treated sediment extracted more P with HCl at the maxima of iron, but was not that much higher compared to P in the untreated sediment.

After anoxic incubation, 

* With the exception of pyrite, all phases have decreased significantly in the top 10 cm after anoxic incubation. Pyrite increased slightly in the non treated cores, but not in the treated ones. (table)

* The layer where iron abundancy is maximal has migrated upwards after anoxic incubating. This holds also for the depth where P/Fe ratio of treated converges with the reference.


```{r seq, echo=FALSE, fig.cap="Iron content of sequential extraction pools as function of depth.", out.width= "50%"}
knitr::include_graphics(c(here("index","figures","seq_extr_Fe_2.eps"), here("index","figures","seq_extr_Fe_3.eps")))
```

```{r Pseq, echo=FALSE, fig.cap="Total phosphorous found in every pool of the sequential extraction, as function of depth.", out.width = "20%"}
knitr::include_graphics(here("index","figures","seq_extr_Fe_3.eps"))
```

 
```{r pwprofiles, echo=FALSE, fig.cap="Depth profile of nutrient concentration in porewater. Treated locations are shown in red, reference locations in blue. Top row shows cores sliced directly after sampling, the bottom row after two months incubating under anoxic conditions. Iron, phosphate, slufide and ammonia were measured with photospectometry, sulfate and nitrate with IC.", out.width = "100%"}
knitr::include_graphics(here("index","figures","profiles.eps"))
```


Dissolved iron is highest at 1 - 10 cm depth in treated cores, and decreases with depth. In contrast, porewater of the non-treated cores contain very little iron. The non treated cores have high concentrations of phosphate in their porewater at every depth, with a peak in concentration close to the surface and an increase with after ~10 cm. Phosphate concentrations in the porewater, however, are low (~1-10 $\mu$M) where the dissolved iron concentration is high, and increase only with depth after 10 cm. 

* An increase in ammonium is seen in the first 10 days in all cores. The non treated cores also show an increase in phosphate. 

* Under anoxic conditions, iron concentrations increase in the treated cores, followed by an increase in phosphate.

* After the initial increase, concentrations of NH4, Fe and P stabilize. The oxic cores show a decrease in P and NH4 levels, and an increase in nitrate concentration. In the anoxic incubations, this is followed by an increase in sulphide in the non treated cores, but not in the treated locations.





* Use tables, figures (but prefer visual presentation):

  + Tables and figures should supplement (and not duplicate) the text.

  + Tables and figures should be provided with legends.

  + _Figure \@ref(fig:graph) shows how to include and reference graphics.
    The graphic must be labelled before. Files must be in __.eps__ format. You
    can do this really easily in R Markdown with `knitr::include_graphics()`_!

  + Figures can be referenced with `\@ref(fig:<name>)`, where `<name>` is the
    name of the code chunk.

```{r incubations, echo=FALSE, fig.cap="Concentration of nutrients in overlying water of incubated cores over time.", out.width = "100%"}
knitr::include_graphics(here("index","figures","IC_incubations_1.eps"))
```
 

```{r PFe, echo=FALSE, fig.cap="The ratio between phosphorous and iron in selected extracion pools. A ratio close to 1 suggests every Fe ion can bind one phosphate.", out.width = "100%"}
knitr::include_graphics(here("index","figures","seq_extr_PFe.eps"))
```


\begin{table}[ht]
\centering
\begin{tabular}{rl|rrrrrrr||rrrr|}
  \toprule
  & \multicolumn{12}{l}{Benthic fluxes in mmol m$^{-2}$ day$^{-1}$} \\
  \hline
  & & \multicolumn{7}{c}{Anoxic incubations} & \multicolumn{4}{c}{Oxic incubations} \\
 & row.names &  \multicolumn{2}{c}{Fe$_{tot}$} & PO$_4^{3-}$ & \multicolumn{2}{c}{NH$_{4}^+$} & HS$^-$ & SO$_4^{2-}$ & 
 PO$_4^{3-}$ & NH$_{4}^+$ & SO$_4^{2-}$ & NO$_3^-$ \\ 
 &  & \textbf{I} & \textbf{III} & \textbf{II} & \textbf{I} & \textbf{III} & \textbf{III} & \textbf{III} & \textbf{II} & \textbf{I} & \textbf{III} & \textbf{III} \\
  \hline
& A & 1.09 & 0.22 & 0.11 & 1.48 & 0.30 & 0.00 & -1.20 & 0.02 & 1.34 & -0.19 & 0.29 \\ 
&  & 0.12 & 0.12 & 0.08 & 0.15 & 0.27 & -0.00 & -1.11 & 0.02 & 0.81 & 0.15 & 0.18 \\ \hline
& B & 0.08 & -0.01 & 0.23 & 1.33 & 0.18 & 0.42 & -0.55 & 0.07 & 0.23 & 0.28 & 0.11 \\ 
&  & 0.01 & -0.01 & 0.33 & 0.96 & 0.19 & 1.15 & -1.23 & 0.24 & 1.08 & 0.38 & 0.17 \\ \hline
& C & 2.90 & 0.14 & 0.10 & 0.94 & 0.25 & 0.02 & -1.42 & 0.01 & 0.27 & 0.23 & 0.03 \\ 
&  & 2.88 & -0.00 & 0.15 & 2.00 & 0.29 & 0.02 & -0.71 & 0.03 & 0.18 & 1.17 & 0.29 \\ \hline
& D & 0.20 & -0.03 & 0.39 & 2.45 & 0.02 & 1.32 & -1.58 & 0.31 & 1.40 & 1.10 & 0.46 \\ 
&  & 0.15 & -0.03 & 0.95 & 3.31 & -0.09 & 1.72 & -0.47 & 0.22 & 0.96 & 0.04 & 0.16 \\ 
   \hline
   \multicolumn{13}{l}{\footnotesize{\textbf{I}: First 10 days}} \\
   \multicolumn{13}{l}{\footnotesize{\textbf{II}: First 25 days}} \\
   \multicolumn{13}{l}{\footnotesize{\textbf{III}: After a week}} \\
   \bottomrule
\end{tabular}
\caption{Calculated benthic fluxes for selected species during incubation. Linear regressions were estimated for certain time intervals (listed with roman numbers), and the slopes are listed. }
    \label{tab:flux}
\end{table}


  + Tables and graphics may appear in the text or in the appendix, especially if
  there are many simulation results tabulated, but is also depends on the study
  and number of tables resp. figures. The key graphs and tables must appear in
  the text!

```{r table, echo=FALSE}
library(tidyverse)
col_names <- c(
  "3m", "6m", "1yr", "2yr", "3yr", "5yr", "7yr", "10yr", "12yr", "15yr"
)
means     <- c(
  3.138, 3.191, 3.307, 3.544, 3.756, 4.093, 4.354, 4.621, 4.741, 4.878
)
stddev    <- c(
  0.915, 0.919, 0.935, 0.910, 0.876, 0.825, 0.803, 0.776, 0.768, 0.762
)
row_names <- c("Mean", "StD")

df <- matrix(data = c(means, stddev), nrow = 2, byrow = T)
rownames(df) <- row_names
colnames(df) <- col_names
df <- data.frame(df)
knitr::kable(
  df,
  booktabs = TRUE,
  caption = "Detailed descriptive statistics of location and dispersion for 2100 observed swap rates for the period from February 15, 1999 to March 2, 2007. Swap rates measured as 3.12 (instead of 0.0312).",
  col.names = col_names, 
  escape = FALSE
) %>%
kable_styling(latex_options = c("HOLD_position")) %>%
row_spec(2, hline_after = T)
```



* Here tables can be easily integrated using the `kable()` function in the
  `knitr` package (with perhaps some additional help from the `kableExtra`
  package). `kable()` will automatically generate a label for the table
  environment. That way you don't have to manually enter in the table in LaTex,
  you can embed tables from R code. 

* Tables can be referenced using `\@ref(label)`, where `label` is `tab:<name>`,
  where `<name>` is the code chunk label.

* The appearance may look different to tables directly typed with LaTex, due to
  limitations in `kable()`. To compare:
    


  + _Equation \@ref(eq:SpecDens) represents the ACs of a stationary
    stochastic process:_
    \begin{equation}
            f_y(\lambda) = (2\pi)^{-1} \sum_{j=-\infty}^{\infty}
                           \gamma_j e^{-i\lambda j}
                         =(2\pi)^{-1}\left(\gamma_0 + 2 \sum_{j=1}^{\infty}
        \gamma_j \cos(\lambda j)\right)
                                       (\#eq:SpecDens)
    \end{equation}
    _where $i=\sqrt{-1}$ is the imaginary unit, $\lambda \in [-\pi, \pi]$ is the
    frequency and the $\gamma_j$ are the autocovariances of $y_t$._

  + Equations can be referenced with `\@ref(eq:<name>)`, where name is defined
    by adding `(\#eq:<name>)` in the line immediately before `\end{equation}`.


