# Results

```{r pwgraphs, echo=FALSE}


# import raw data


IC_raw_data <- read_excel(path.expand(here("index","data", "IC_raw_data.xlsx")))
pw_photometric <-  read_excel(path.expand(here("index","data", "pw_P_photometric.xlsx")))

# Transform the raw data to middle duplicates.
ICplotdata  <- IC_raw_data %>% 
  filter(str_detect(sample,"pw|sw")) %>% 
  group_by(sample) %>% 
  mutate(P = (mean(Phosphate)*1000)/94.9714, "SO" = mean(Sulphate)*1000/96.06, NO = mean(Nitrate)*1000/62.004, "Br" = mean(Bromide)*1000/79.9, "Fl" = mean(Fluoride)*1000/19, "Cl" = mean(Chloride)*1000/35.45 ) %>%
  distinct(sample, .keep_all = TRUE) %>% 
  mutate(treated =
      case_when(
        str_detect(sample,"A|C")  ~ "treated",
        str_detect(sample,"B|D")  ~ "nontreated")) %>% left_join(
  pw_photometric,
  by = c("sample" = "Sample"),
  copy = FALSE,
  suffix = c(".IC", ".photometric"),
  keep = FALSE
) %>%  group_by(location) %>% arrange(cm_below_swi) 

# reshape data.
molten_IC_core_data <- ICplotdata %>% select("location", "sample", "cm_below_swi", "SO" : "treated") %>% 
melt(id.vars = c("location", "sample", "cm_below_swi", "treated"), 
     measured_.vars = c(  
                         "SO", 
                         "NO",
                         "Br",
                         "Fl", 
                         "Cl"), na.rm = TRUE)

nest_IC_pw_depth <- molten_IC_core_data %>% group_by(variable) %>% nest()

# plot profiles by parameter

Lables = as_labeller( c( "P"  = "PO[4]^'3-'",                      
   "SO" = "SO[4]^'2-'", 
   "NO" = "NO[3]^'-'",
   "Br" = "Br^'-'",
   "Fl" = "F^'-'", 
   "Cl" = "Cl^'-'"), default =  label_parsed )

IC_profile_plots <- ggplot(molten_IC_core_data, mapping = aes(
                        x = value,
                        y = cm_below_swi ,
                        color = location,
                        shape = location)
         ) +
       
       scale_color_manual( values=c("A" = "red", "B" = "blue", "C" = "red", "D" = "blue")) +
       scale_shape_manual( values=c("A" = 16, "B" = 1, "C" = 17,  "D" = 2)) +
      scale_y_reverse() +
       geom_point() + 
       geom_path() +
       facet_grid(cols = vars(variable), scales = "free_x", labeller = Lables) +
       labs(  x = expression(paste("concentration in ",mu,"mol/L")), 
              y = "Depth in cm",
              title = "pw profiles measured with IC") +
      theme_classic() +
      theme(aspect.ratio = 2. ,
            axis.text.y   = element_text(size=14),
            axis.text.x   = element_text(size=14),
            axis.title.y  = element_text(size=14),
            axis.title.x  = element_text(size=14),
            strip.text.y   = element_text(size=14),
            strip.text.x   = element_text(size=14),
            panel.background = element_blank(),
            panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(),
            axis.line = element_line(colour = "black"),
            panel.border = element_rect(colour = "black", fill=NA, size=1)
            )

ggsave(paste("IC_profiles.png",sep=""), plot =IC_profile_plots, path = path.expand(here("index","figures")),

       width =30, height = 18,units = "cm",dpi = 600)

```



``` {r ICinc, echo = FALSE}

incubationgraph <- read_excel(here("index","data","incubationgraph.xlsx"))

# middle duplicates for IC data
IC_inc_data <- 
  IC_raw_data %>% 
  filter(str_detect(sample,'inc')) %>% 
  group_by(sample) %>% 
  mutate(P = (mean(Phosphate)*1000)/94.9714, 
         "SO" = mean(Sulphate)*1000/96.06, 
         NO = mean(Nitrate)*1000/62.004, 
         "Br" = mean(Bromide)*1000/79.9, 
         "Fl" = mean(Fluoride)*1000/19,
         "Cl" = mean(Chloride)*1000/35.45) %>% 
  distinct(sample, .keep_all = TRUE) 


# Join IC and photometric data, and add treated and oxic status foor all cores.
inc_data <- 
full_join(
  incubationgraph,
  IC_inc_data,
  by = c("samplenr" = "sample"),
  copy = FALSE,
  suffix = c(".photometric", ".IC"),
  keep = FALSE
) %>% 
  mutate(oxic_state =
      case_when(
        str_detect(samplenr,"2\\.")  ~ "oxic",
        str_detect(samplenr,"3\\.")  ~ "anoxic")) %>% 
  mutate(treated =
      case_when(
        str_detect(samplenr,"A|C")  ~ "treated",
        str_detect(samplenr,"B|D")  ~ "nontreated"))  %>% 
  mutate(Location =
      case_when(
        str_detect(samplenr,"A")  ~ "A",
        str_detect(samplenr,"-B")  ~ "B",
        str_detect(samplenr,"-\\C")  ~ "C",
        str_detect(samplenr,"-\\D")  ~ "D")) 

# reshape the data by melting all variables, and grouping them by parameter.

molten_inc <- inc_data %>% select("Core.photometric", 
                                  "samplenr",
                                  "time", 
                                  "H2SuM", 
                                  "FeTot(uM)", 
                                  "Preal(uM)", 
                                   "NH4", 
                                   "SO",
                                   "NO",
                                  "oxic_state", 
                                  "treated", 
                                  "Location") %>% 
melt(id.vars = c("Core.photometric","samplenr","time", "oxic_state", "treated","Location"), 
     measured_.vars = c( "H2SuM", 
                         "FeTot(uM)", 
                         "Preal(uM)", 
                         "NH4", 
                         "SO",
                         "NO"), na.rm = TRUE)

nest_inc <- molten_inc %>% group_by(variable) %>% nest()

# create plots for all parameters
Lables = as_labeller( c(  "H2SuM" = "HS^'-'", 
                          "FeII(uM)" = "Fe^'2+'",
                          "FeTot(uM)" = "Fe[tot]", 
                          "FeIII(uM)" = "Fe^'3+'",  
                          "Preal(uM)" = "PO[4]^'3-'",
                          "NH4" = "NH[4]^'+'",
                          "P"  = "PO[4]^'3-'",                      
                          "SO" = "SO[4]^'2-'", 
                          "NO" = "NO[3]^'-'",
                          "Br" = "Br^'-'",
                          "Fl" = "F^'-'", 
                          "Cl" = "Cl^'-'"), default =  label_parsed )

IC_incubation_graph <- 
  ggplot(molten_inc, 
       mapping = aes(x = time , 
                     y = value, 
                     color = treated, 
                     shape = Location, 
                     by = Core.photometric)
       ) + 
  scale_color_manual( values=c("treated" = "red", "nontreated" = "blue")) +
  scale_shape_manual( values=c("A" = 16, "B" = 1, "C" = 17,  "D" = 2)) +
  geom_point() + 
  geom_line() + 
  theme(aspect.ratio = 0.5,
        axis.text.y   = element_text(size=14),
        axis.text.x   = element_text(size=14),
        axis.title.y  = element_text(size=14),
        axis.title.x  = element_text(size=14),
        strip.text.y   = element_text(size=14),
        strip.text.x   = element_text(size=14),
        
        panel.background = element_blank(),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1)
        ) + 
  facet_grid(variable ~ oxic_state, scales = "free_y",switch = "y", labeller = Lables) + labs(title = "Incubations", x= "time (days)", y = expression(paste("concentration in ",mu,"mol/L")))

ggsave(paste("IC_incubations.png",sep=""), plot =IC_incubation_graph, path = path.expand(here("index","figures")),

       width =20, height = 20,units = "cm",dpi = 600)

```



```{r Feseq, echo=FALSE}
#import sequential extraction data.
Seq_extr_data <- read_excel(here("index","data","Seq_extr_data.xlsx"))


# define detection limits as given by ICP report
Detlim_Fe_MgCl <- 0.068
Detlim_Fe_HCl <- 0.021
Detlim_Fe_HNO <- 0.035
Detlim_P_Mg <- 0.097
Detlim_P_HCl <- 0.043
Detlim_P_HNO <- 0.057

# density of extractants and molar weight of Fe and P
d_MgCl <- 1.0467
d_pyroP <- 1.0402
d_HCl <- 1.0152
d_CBD <- 1.0887
d_HNO <- 1.414
mw_Fe <- 55.845
mw_P <- 30.973762


# define functions to calculate umol/g sediment from raw ICP and colourimetric data.
ppm_to_umol_p_g <- function(mol_weight, 
                            Dens, 
                            total_weight, 
                            sample_weight, 
                            Dil = 10, 
                            detlim, 
                            ppm){
  
 conc <- case_when(ppm/Dil < detlim ~ 0, 
                   T ~ ((total_weight/Dens)*ppm)/(sample_weight*mol_weight) 
                    )
 return(conc)
}

mM_to_umol_p_g<- function(  Dens, 
                            total_weight, 
                            sample_weight,
                            mM){
  
 conc <- case_when(mM < 0 ~ 0,
                   T ~ ((total_weight/Dens)*mM)/(sample_weight) )
                    
 return(conc)
}

# Transform raw data.
Seq_extr_data %>% 
  mutate(
    Location = case_when(
        str_detect(Station,"A")  ~ "A",
        str_detect(Station,"B")  ~ "B",
        str_detect(Station,"C")  ~ "C",
        str_detect(Station,"D")  ~ "D",
        T ~ "blank"),
    Incubation = case_when(
        str_detect(Station, "1\\.") ~ "before",
        str_detect(Station, "3\\.")  ~ "after",
        T ~ "blank" ),
    Fe_MgCl_A_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_MgCl, 
                                  total_weight = weight_MgCl_A, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_MgCl,
                                  ppm = ICP_MgCl_A_Fe),
    Fe_MgCl_B_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_MgCl, 
                                  total_weight = weight_MgCl_B, 
                                  sample_weight = sample_weight_B, 
                                  detlim = Detlim_Fe_MgCl,
                                  ppm = ICP_MgCl_B_Fe),
    Fe_pyroP_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_pyroP,
                                  Dil = 20,
                                  total_weight = weight_pyroP, 
                                  sample_weight = sample_weight_B, 
                                  detlim = Detlim_Fe_HNO,
                                  ppm = ICP_pyroP_Fe),
    Fe_HCl_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_HCl, 
                                  total_weight = weight_HCl, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_HCl,
                                  ppm = ICP_HCl_Fe),
    Fetot_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_Fetot),
    FeII_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_FeII),
    FeIII_HCl_calc = mM_to_umol_p_g(Dens = d_HCl,
                                    total_weight = weight_HCl,
                                    sample_weight = sample_weight_A,
                                    mM = Col_HCl_FeIII),
    Fe_HNO_calc = ppm_to_umol_p_g(mol_weight = mw_Fe, 
                                  Dens = d_HNO, 
                                  total_weight = weight_HNO, 
                                  sample_weight = sample_weight_A, 
                                  detlim = Detlim_Fe_HNO,
                                  ppm = ICP_HNO_Fe*10),
    ) %>% view()

```

* Organize material and present results.

* Use tables, figures (but prefer visual presentation):

  + Tables and figures should supplement (and not duplicate) the text.

  + Tables and figures should be provided with legends.

  + _Figure \@ref(fig:graph) shows how to include and reference graphics.
    The graphic must be labelled before. Files must be in __.eps__ format. You
    can do this really easily in R Markdown with `knitr::include_graphics()`_!

  + Figures can be referenced with `\@ref(fig:<name>)`, where `<name>` is the
    name of the code chunk.

```{r graph, echo=FALSE, fig.cap="Estimated residuals from model XXX. ...", out.width = "50%"}
knitr::include_graphics(here("index","figures","graph.eps"))
```
  + Tables and graphics may appear in the text or in the appendix, especially if
  there are many simulation results tabulated, but is also depends on the study
  and number of tables resp. figures. The key graphs and tables must appear in
  the text!

```{r table, echo=FALSE}
library(tidyverse)
col_names <- c(
  "3m", "6m", "1yr", "2yr", "3yr", "5yr", "7yr", "10yr", "12yr", "15yr"
)
means     <- c(
  3.138, 3.191, 3.307, 3.544, 3.756, 4.093, 4.354, 4.621, 4.741, 4.878
)
stddev    <- c(
  0.915, 0.919, 0.935, 0.910, 0.876, 0.825, 0.803, 0.776, 0.768, 0.762
)
row_names <- c("Mean", "StD")

df <- matrix(data = c(means, stddev), nrow = 2, byrow = T)
rownames(df) <- row_names
colnames(df) <- col_names
df <- data.frame(df)
knitr::kable(
  df,
  booktabs = TRUE,
  caption = "Detailed descriptive statistics of location and dispersion for 2100 observed swap rates for the period from February 15, 1999 to March 2, 2007. Swap rates measured as 3.12 (instead of 0.0312).",
  col.names = col_names, 
  escape = FALSE
) %>%
kable_styling(latex_options = c("HOLD_position")) %>%
row_spec(2, hline_after = T)
```

* Allows the reader to judge whether the sample is biased or to evaluate 
  possible impacts of outliers, for example.

* Here tables can be easily integrated using the `kable()` function in the
  `knitr` package (with perhaps some additional help from the `kableExtra`
  package). `kable()` will automatically generate a label for the table
  environment. That way you don't have to manually enter in the table in LaTex,
  you can embed tables from R code. 

* Tables can be referenced using `\@ref(label)`, where `label` is `tab:<name>`,
  where `<name>` is the code chunk label.

* The appearance may look different to tables directly typed with LaTex, due to
  limitations in `kable()`. To compare:
    \begin{table}[ht]

    \begin{center}
        {\footnotesize
        \begin{tabular}{l|cccccccccc}
            \hline \hline
                      & 3m    & 6m    & 1yr   & 2yr   & 3yr   & 5yr   & 7yr   & 10yr  & 12yr  & 15yr   \\
            \hline
                Mean   & 3.138 & 3.191 & 3.307 & 3.544 & 3.756 & 4.093 & 4.354 & 4.621 & 4.741 & 4.878  \\
                StD    & 0.915 & 0.919 & 0.935 & 0.910 & 0.876 & 0.825 & 0.803 & 0.776 & 0.768 & 0.762  \\
            \hline \hline
        \end{tabular}}
    \end{center}
    \caption{This table was handwritten with LaTeX.}
    \label{tab:table2}
    \end{table}

* R Markdown can also supports math equations just like _LaTeX_!

  + _Equation \@ref(eq:SpecDens) represents the ACs of a stationary
    stochastic process:_
    \begin{equation}
            f_y(\lambda) = (2\pi)^{-1} \sum_{j=-\infty}^{\infty}
                           \gamma_j e^{-i\lambda j}
                         =(2\pi)^{-1}\left(\gamma_0 + 2 \sum_{j=1}^{\infty}
        \gamma_j \cos(\lambda j)\right)
                                       (\#eq:SpecDens)
    \end{equation}
    _where $i=\sqrt{-1}$ is the imaginary unit, $\lambda \in [-\pi, \pi]$ is the
    frequency and the $\gamma_j$ are the autocovariances of $y_t$._

  + Equations can be referenced with `\@ref(eq:<name>)`, where name is defined
    by adding `(\#eq:<name>)` in the line immediately before `\end{equation}`.

## Review of Results

*  Do the results support or do they contradict theory ?

*  What does the reader learn from the results?

*  Try to give an intuition for your results.

*  Provide robustness checks.

*  Compare to previous research.
