# Results


```{r swcalc, include = FALSE, echo=FALSE}

EC_A <- c(434,	449,	433)
EC_B <- c(446,	456,	451)
EC_C <- c(379,	408,	400)
EC_D <- c(392,	397,	402)
EC <- list(EC_A, EC_B, EC_C, EC_D)

for (i in 1:4) {
 m = mean(EC[[i]])
 s = sd(EC[[i]])
 print(m)
 print(s)
  
}

t.test(EC_A, EC_B)
t.test(EC_C, EC_D)
t.test(c(EC_A, EC_B),c(EC_C, EC_D))
```

## Surface water

The surface water measured \textit{in situ} at both the treated and non treated locations had dissolved oxygen concentrations of 9.5-10.5 mg/L and pH levels of around 8. While no significant difference between treated and non-treated locations, water conditions did vary between the locations closer (C and D) and further away (A and B) from the water inlet, due to a  significantly higher electric conductivity at locations A and B ($438\pm9\mu$S and $451\pm5\mu$S), than measured at locations C and D ($395\pm15\mu$S and $397\pm5\mu$S).  




```{r seq, echo=FALSE, fig.cap="Sequential extraction results. The extracted Fe and P for each extraction step is plotted as function of depth. Left panel shows the extracted Fe in each pool, the right panel the P.  The stacked and coloured integrals represent the relative size of the corresponding extacted pool and the total width the sum of all pools. The pyrophosphate extraction was performed in parallel, and is substracted from the HCl pool in the Fe data.   ", fig.show="hold", out.width= "45%"}
grap <- c(paste(here("index","figures","seq_extr_Fe_2.png")), paste(here("index","figures","seq_extr_Fe_3.png")))
include_graphics(grap)
```

## Sediment analysis

Addition of Fe-containing by-products resulted in significantly higher Fe content of the sediments. The untreated sediment contains about 2wt\% of Fe uniformly distributed over depth, whereas the Fe content in the treated sediment varies considerably with depth and reaches up to 25wt\% at certain intervals, but is mainly found in the shallow (<10cm) sediment. In total, the first 10cm of sediment of the treated cores contain 1550mg and 3580mg (cores from locations A and C, respectively) of Fe, significantly higher than the Fe content of the non-treated cores which in the top 10cm adds up to 490mg and 590mg (cores from locations B and D, respectively).

In figure \@ref(fig:seq), left panel, which shows Fe concentrations acquired by sequential extraction, is shown that the largest Fe pool extracted in the treated sediment is the HCl extractable pool (average 50-60\% of total Fe in top 10cm), in contrast to untreated sediment, where the HCl extracted Fe is only about 10\% of the total Fe in the 10 cm, and most Fe is extracted by HNO$_3$ (40-60\%). The HNO$_3$ extracted Fe content is constant with depth in all cores (116-223 $\mu$mol g$^{-1}$, $\sigma=$ 25 $\mu$mol g$^{-1}$), and independent of variations in total Fe. In contrast, values of extracted Fe in all fractions except HNO$_3$ peak within the first 10cm of sediment, then decrease with depth. This amounts to average amounts of Fe extracted in the non-treated cores by HCl, pyrophosphate and CBD extractions  2-10 times higher in the top 10cm (HCl: 54 $\pm$ 22 $\mu$mol g$^{-1}$; pyrophosphate: 12 $\pm$ 7 $\mu$mol g$^{-1}$; CBD: 20 $\pm$ 6 $\mu$mol g$^{-1}$) than in deeper sediment (HCl: 18 $\pm$ 11 $\mu$mol g$^{-1}$; pyrophosphate: 2.5 $\pm$ 2.1 $\mu$mol g$^{-1}$; CBD: 13 $\pm$ 4 $\mu$mol g$^{-1}$), and in the treated cores approximately 20 times more (*shallow* HCl: 840 $\pm$ 520 $\mu$mol g$^{-1}$; pyrophosphate: 123 $\pm$ 55 $\mu$mol g$^{-1}$; CBD: 240 $\pm$ 160 $\mu$ mol g$^{-1}$;    *deep* HCl: 36 $\pm$ 30 $\mu$mol g$^{-1}$; pyrophosphate: 6 $\pm$ 7 $\mu$mol g$^{-1}$; CBD: 17 $\pm$ 7 $\mu$mol g$^{-1}$). The size of all Fe pools other than HNO$_3$ is proportional to the total Fe content with a relatively stable distribution between the pools: For the non-treated shallow 10cm of sediment the average molar ratio between the HCl, pyrophosphate and CBD pools is respectively  6:1:2, though deeper in the sediment this ratio changes gradually in favor of the CBD pool (MgCl$_2$ pools are negligible, and often below the detection limit). The treated sediment has an average HCl-pyrophosphate-CBD ratio of 7:1:2 in the top 10cm, which means the treated cores contain relatively more HCl extractable Fe compared to the untreated sediment. 

In addition to sediment from cores which were sliced and processed directly after the field campaign, selected cores used in the benthic flux experiment were partly sliced  and analyzed by sequential extraction after the experiment ended, of which the results are shown in the right columns in figure \@ref(fig:seq). HNO$_3$ extracted Fe content in non-treated cores are roughly 20\% higher after anoxic incubation than in the fresh cores, while the HCl and pyrophosphate pools are 5-50\% smaller. 


Phosphate extracted during the sequential extractions correlates with the total Fe content, and with the HCl pool. Most P (30-50\% of total P) is extracted by HCl in all cores. In the treated cores this is the largest pool of Fe as well, but HCl extracted Fe is just a small fraction in the non-treated cores, still the extracted P is largest in this pool. (Fig. \@ref(fig:seq), right panel)  The treated sediment contain more P extracted with HCl than the untreated sediment (on average 20-100% more at shallow depth; respectively 54-75mg and 33-48mg total P), particularly at depths where the Fe content is highest, but the contrast is not as large as for the Fe content, which can be an order of magnitude larger.

 
```{r pwprofiles, echo=FALSE, fig.cap="Porewater concentrations as function of depth. The plots share the y axis which represents the sediment depth, while the x axes are scaled individually for each dissolved species. Cores from treated locations are shown in red, non-treated reference locations in blue. Top row shows cores sliced directly after sampling, the bottom row after two months incubating under anoxic conditions. Iron, phosphate, slufide and ammonia were measured with photospectometry, sulfate and nitrate with IC.", out.width = "100%"}
knitr::include_graphics(here("index","figures","profiles.eps"))
```

## Porewater analysis

Similar to the solid phase composition, addition of Fe containing by-products was also reflected in the composition of the sediment pore waters. Porewater of the non-treated cores contain very little Fe (< 10 $\mu$M), but porewater Fe concentrations in the treated cores were high (>30 $\mu$M up to 350 $\mu$M, see fig. \@ref(fig:pwprofiles))  at depths with high solid iron content, and found in both the 2+ and 3+ oxidation state. The ratio Fe$^{3+}$/Fe$^{2+}$ in the top 10 cm is relatively high and exceeds 1 at certain depths. Concurrent with the solid Fe content, dissolved iron is highest at 1 - 10 cm depth, and subsequently decreases with depth. Below this sediment layer where solid iron is concentrated, dissolved Fe in the porewater is predominantly found as Fe$^{2+}$. 

Phosphate concentrations in the porewater exhibit a trend opposite to that of Fe: P concentrations in porewater of non-treated cores are much higher (20-240 $\mu$M) than in the treated cores, where P concentrations are low (< 5 $\mu$M). Similar to the P concentration decrease as result of added Fe, sulfide concentrations are considerably lower in treated cores (< 1 $\mu$M), opposed to high sulfide concentrations in the porewater of untreated sediment (5-100 $\mu$M).  This effect persists deep in the core, below the shallow zone where sediment is enriched with Fe.
In addition, the decrease in sulfate concentration with depth in the porewater was steeper in locations C and D compared to A and B.( Fig. \@ref(fig:pwprofiles))


```{r incubations, echo=FALSE, fig.cap="Time evolution of the concentrations of solutes in overlying water of incubated cores. Cores with anoxic conditions induced during the experiment (left colum) are compared with cores kept oxic by continue aeration (right column). The main goal was to study the difference in benthic fluxes from treated sediment, here in red, in relation to untreated sediment, displayed in blue. There are two treated and two untreated locations,  every location is incubated in duplo. The scale of the y axis is different for each parameter, while the x axis representing time in days is the same for all.", out.width = "85%"}
knitr::include_graphics(here("index","figures","IC_incubations_1.eps"))
```
 
## Benthic flux measurements

The benthic flux experiment shows that Fe treatment changes the release of P and Fe significantly over time, as P release is suppressed while Fe increase is enhanced. The increase of P over time was highest in non-treated cores, and remain much lower in surface water of treated cores. Furthermore, lowering the  redox conditions of the overlying water increases P release. Fe release from the treated sediment is dependent on redox conditions as well, and is highest in the anoxic cores. The increase in Fe in the treated cores is characterized by high flux (1-3 mmol m$^{-2}$ day$^{-1}$) at the start of the experiment, followed by a much lower flux after 1-2 weeks (Fig. \@ref(fig:incubations)). The non-treated cores on the other hand, exhibit much lower, but still significant Fe fluxes, particularly in the D core, where they reach up to 200 $\mu$mol m$^{-2}$ day$^{-1}$ (Table \@ref(tab:flux)). An initial increase in Fe concentration is in the non-treated cores is followed by a gradual decrease, while at the same time the sulfide concentration increases. The increase in sulfide in low redox conditions is coupled with a decrease in sulfate concentration. Sulfide concentrations are not increasing in th treated cores, though sulfate concentration decreases at the same rate as in the non-treated cores under anoxic conditions (0.6-1.6 mmol m$^{-2}$ day$^{-1}$). Finally,  nitrogen, in the form of ammonium (NH$_4^+$) and nitrate (NO$_3^-$), is less influenced by the treatment. After an initial high ammonium flux (1-3 mmol m$^{-2}$ day$^{-1}$), the increase slows down, and with oxygen available, nitrification dominates in the oxic cores. While this pattern is found in all cores, the ammonium production rate appears to be smaller during the initial rise, but larger during the long-term increase in the treated cores.



\begin{table}[ht]
\centering
\begin{tabular}{rl|rrrrrrr||rrr|}
  \toprule
  & &\multicolumn{10}{l}{\textbf{Benthic fluxes in mmol m$^{-2}$ day$^{-1}$}} \\
  \hline
  & & \multicolumn{7}{c}{Anoxic incubations} & \multicolumn{3}{c}{Oxic incubations} \\
 &  &  \multicolumn{2}{c}{Fe$_{tot}$} & PO$_4^{3-}$ & \multicolumn{2}{c}{NH$_{4}^+$} & HS$^-$ & SO$_4^{2-}$ & 
 PO$_4^{3-}$ & NH$_{4}^+$ &  NO$_3^-$ \\ 
 & \footnotesize{Time interval:} & \textbf{I} & \textbf{III} & \textbf{II} & \textbf{I} & \textbf{III} & \textbf{III} & \textbf{III} & \textbf{II} & \textbf{I} &  \textbf{III} \\
  \hline
& A & 1.09$\ast$ & 0.22 & 0.11 & 1.48 & 0.30 & 0.00 & -1.20 & 0.02 & 1.34 &  0.29 \\ 
&  & 0.12$\ast$  & 0.12$\ast$ & 0.08 & 0.15$\ast$ & 0.27 & -0.00$\ast$ & -1.11 & 0.02 & 0.81 &  0.18 \\ \hline
& B & 0.08$\ast$ & -0.01$\ast$ & 0.23 & 1.33 & 0.18 & 0.42 & -0.55$\ast$ & 0.07 & 0.23$\ast$ &  0.11 \\ 
&  & 0.01$\ast$ & -0.01$\ast$ & 0.33 & 0.96 & 0.19 & 1.15 & -1.23$\ast$ & 0.24 & 1.08 & 0.17$\ast$ \\ \hline
& C & 2.90 & 0.14 & 0.10 & 0.94 & 0.25 & 0.02 & -1.42 & 0.01 & 0.27$\ast$ &  0.03$\ast$ \\ 
&  & 2.88 & -0.00$\ast$ & 0.15$\ast$ & 2.00 & 0.29 & 0.02 & -0.71$\ast$ & 0.03 & 0.18$\ast$ &  0.29 \\ \hline
& D & 0.20$\ast$ & -0.03 & 0.39$\ast$ & 2.45 & 0.02$\ast$ & 1.32 & -1.58$\ast$ & 0.31 & 1.40$\ast$  & 0.46 \\ 
&  & 0.15$\ast$ & -0.03 & 0.95 & 3.31 & -0.09$\ast$ & 1.72 & -0.47$\ast$ & 0.22 & 0.96  & 0.16 \\ 
   \hline
   & & \multicolumn{10}{l}{\scriptsize{$\ast$ T test P value of linear model slope above 0.05}} \\
   \multicolumn{12}{l}{\footnotesize{\textbf{I}: First 10 days}} \\
   \multicolumn{12}{l}{\footnotesize{\textbf{II}: First 25 days}} \\
   \multicolumn{12}{l}{\footnotesize{\textbf{III}: After a week}} \\
   \bottomrule
\end{tabular}
\caption{Estimations of benthic fluxes for selected species during incubation on various timescales. The fluxes are computed by deriving the slope of a linear regression over time within certain time intervals, which can be found in the table by roman numbers. The different time intervals were chosen based on periods with relatively constant increase observed in the incubation data. Important to note is that the calculated fluxes have a high degree of uncertainty, the values with an asterix are statistically not significantly different from 0.}
    \label{tab:flux}
\end{table}
